Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-05-22 article.qmd
update figure
chore: Update notebooks, remove unnecessary files

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - href: ../
    text: Website
  - repo
  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
    text: Tana
  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
    text: Overleaf
abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase. We identify and analyze the properties of the discontinuities at different radial distances from the Sun. By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
---

@@

<!-- ![](figures/juno_orbit_white){#fig-orbit width=85%} -->

<!-- ![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot} -->

@@

{{< embed notes.ipynb#tbl-missions >}}

>>>>

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - href: ../
    text: Website
  - repo
  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
    text: Overleaf

abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase. We identify and analyze the properties of the discontinuities at different radial distances from the Sun. By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
---

@@

@@

<!-- 
{{< embed notes.ipynb#tbl-missions >}}
 -->

### 2024-05-22 index.qmd
update
update figure
chore: Update notebooks, remove unnecessary files

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
---

@@

@@

>>>>

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
code-links:
  - href: zotero://select/library/collections/WS2YQQZB
    text: Zotero
  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
    text: Tana
---

@@

# Dataset, models, and methods

@@

## Occurrence rate

![](figures/ocr/ocr_time_cleaned)

## Properties

![](figures/l_j_fit_xscale_log.png)

# Appendix

![Time resolution effect](figures/method/time_res_effect.png)

![Tau effect](figures/method/tau_effect.png)
